Deciding to Disclose

### 2015-06-02 Model.tex
Add simple bayes e.g.

@@

\begin{equation}
R_{m}(s_{w}, s_{m}) = \sum_{i\in \Theta} -u_{w}(s_{w}, s_{m}, i)p(i | s_{w})
\end{equation}

>>>>

If we take our light drinker from the lexicographic case, and assume that they began with an uninformative prior. The 6 possible signal-payoffs pairings are then \([(l,10),(m,10),(h,10),(m,9),(h,9),(h,8)]\), with \(\alpha_{i}=1\) for all \(i\). After playing the three rounds, \(n_{l,10}=2\), and \(n_{m,9}=1\).

The agent then evaluates \(R_{w}\) for each signal, e.g. for the light signal:

\begin{equation*}
\begin{align*}
X &= \{10\}\\
R_{w}(l) &= \sum_{x \in X} -xp(x | l) &= -10p(10 | l)\\
R_{w}(l) &= -10(\frac{\alpha_{l,10}+n_{l,10}}{\sum_{j}(\alpha_{j}+n_{j})}) &= -10(\frac{1+2}{1+2})\\
R_{w}(l) &= -10(\frac{3}{3}) &= -10
\end{align}
\end{equation}

and by the same method, \(R_{w}(m)=-7\), and \(R_{w}(h)=-9\), concluding that signalling honestly is the best move.

@@

\begin{equation}
R_{m}(s_{w}, s_{m}) = \sum_{i\in \Theta} -u_{m}(s_{w}, s_{m}, i)p(i | s_{w})
\end{equation}

Returning to our example agent, we now add slightly more information, and stipulate that they have in fact encountered a harshly judgemental midwife in all three rounds, hence \(n_{h}=3\). Their prior beliefs remain uninformative, i.e. \(\alpha_{j} = 1, j \in \{l,m,h\}\), \(\alpha_{i}=1,i \in \{r,n\}\). As before, the agent evaluates \(R_{w}\) for the three signals, and the process for the light signal is given below -

\begin{equation*}
\begin{align*}
R_{w}(s_{w}, l) &= \sum_{i\in A_{m}}\sum_{j\in \Theta} -u_{w}(s_{w}, i, l, j)p(j)p(i | s_{w}),
R_{w}(s_{w}, l) &= 
\end{align}
\end{equation}
